Tutorials: A Brief Overview

### 2023-04-27 index.qmd
landing page updates

---
#title: "Temporary Landing Page for Longitudinal Project"
#format:
#  html:
#    css: styles.css
#    theme: cosmo
#    fontsize: 1.1em
    #linestretch: 1.7
---

<div class="text-3xl text-center">
This is the temporary landing page for the Longitudinal Analysis Project. <br> The site is currently under construction and used for testing purposes only. <br> Contents may be inaccurate.
</div>

<br>

::: {.grid}

::: {.g-col-2}
:::

::: {.g-col-8}
![](./figures/lights.png)
:::

::: {.g-col-2}
:::

:::

</div>

>>>>

---
#title: "Longitudinal Analysis"
format:
  html:
    page-layout: full
    grid:
      sidebar-width: 0px
      body-width: 2000px
      margin-width: 0px
      gutter-width: 1.5rem
---

![](./figures/Figlanding4.svg)

### 2023-04-27 temp.qmd
landing page updates

---
title: "Tutorials: A Brief Overview"
number-sections: true
format:
 html:
   css: styles.css
   theme: cosmo
   fontsize: 1.1em
   linestretch: 1.7
---

This is the TUTORIAL main page example.

## Main Section

@@

>>>>

---
title: "Tutorials: A Brief Overview"
format:
  html:
    page-layout: full
    grid:
      sidebar-width: 0px
      body-width: 2000px
      margin-width: 0px
      gutter-width: 1.5rem
#    css: styles.css
#    theme: cosmo
#    fontsize: 1.1em
#    linestretch: 1.7

---

![FigmaLandingTest2](./figures/Figlanding3.svg)

<div class="page-layout-custom">
  ![FigmaLandingTest2](./figures/Figlanding2.svg)
</div>

xxxxx
It is important to match a theory of change with design and statistical model to assess change. (p. 4)
Models with two time points cannot provide estimates of within-person change.
“Stability” over time can reflect many things, only some of which mean a lack of change. (p. 14)
It is helpful to describe not only average growth (e.g. intercept and slope means), but variances in the growth parameters. (p. 25)

Models that focus exclusively on mean-level change sometimes called Marginal Models
Those that emphasize individual change often do so through inclusion of Random Effects
often called “growth models”

Longitudinal Psychometrics

xxxxxx

@@

::: {style="text-align: justify; text-align: center; line-height: normal; color: white; border: solid black; background-color: darkgoldenrod; padding: 70px; font-family: Georgia, serif;"}

This is the temporary landing page for the Longitudinal Analysis Project. <br> The site is currently under construction and used for testing purposes only. <br> Contents may be inaccurate.

</div>
